Dependent Object Types

### 2012-08-31 doc/candidacy/report.tex
minor
abstract

% TODO

@@

In terms of theoretical results, the paper confirms the type soundness
of the calculus and the undecidability of its type checking.

>>>>

Our aim is to propose a new type-theoretic foundation of Scala based
on a core calculus for path-dependent types. Towards this end, we
review three papers presenting calculi in which path-dependent types
are essential: a calculus for first-class translucent ML-like modules,
the Tribe calculus for virtual classes, and the ${\nu}Obj$ calculus
for reasoning about classes and objects with type members.

@@

In terms of theoretical results, the paper confirms the type soundness
of the calculus and the undecidability of its type checking by
reduction to $F_{<:}$.
